---
title: "Whale"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Whale}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warnings = FALSE, 
  messages = FALSE, 
  prompt = FALSE,
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

Whale-come! This R package was inspired by [cowsay](https://github.com/sckott/cowsay) and [praise](https://github.com/rladies/praise). I hope this package made you smile today! 

## First things first

`Whale` is a toy project and is still under development. You can install the latest version from [GitHub](https://github.com/) with:

```{r, install, results = "hide", eval = FALSE}
# install.packages("remotes")
remotes::install_github("fontikar/ohwhaley")
remotes::install_github("lgurrin/Whale")
```

## Take it for a spin

`Whale` contains one function only. `say()` will echo a randomly chosen whale-themed phrase for your enjoyment.

```{r example}
library(Whale)
 
say() 
```

Alternatively, you can supply your own phrase

```{r, customise}
say("I'm beached as bro!!!")
```
